# Using renv {#renv}

## Basic workflow

- Create a chapter Rmd in root
- Create a chapter folder in root
- Create a renv environment for that chapter with `renv_new.R`
- Activate the renv env for a given chapter by running the code block below.
This is not done automatically as there will be multiple renv envs for the book
(one per chapter) and you don't know which one you want at a given time.
- Start writing content in child Rmds in chapter folder
- If you need specific package versions not installed on your system R then 
install explicitly in the env with e.g. `renv::install("dplyr@0.8.5")`.
- When in the renv env, run `renv_snapshot.R` occasionally.
- Be sure to use `renv_unload.R` when you are done working on a chapter.
- Before building the book locally (which is done by knit and merge method, i.e. knitting
each chapter individually) you'll need to run `renv_restore.R` for each chapter
individually.

## Targets

Currently, to build the entire book on another completely fresh computer/using GHA, you'd have
to use `renv_restore.R` for each chapter to install the dependencies for each
chapter and only then could you run `rmarkdown::render_site()` wherein each
chapter is knitted individually (and `renv::load()` is called for each chapter 
so that it is knitted with its dependencies) and the result is merged.

Here is where I think targets would come in handy wherein you check if the 
chapter has changed and if it hasn't don't run `renv_restore.R`? Actually no,
because there is no way for `rmarkdown::render_site()` to just knit certain
files.

## GHA

2 options:

1. Build book locally, commit built book and just deploy _book directory using Github pages.
I'll probably just do this because I am lazy. Use renv profiles per chapter (like here https://github.com/matt-dray/rostrum-blog/commit/b06036b87dba5096664294a66f2eec2d32bb1963).
2. Make a GHA to build book based off of the standard bookdown workflow
(https://github.com/r-lib/actions/blob/v1/examples/bookdown.yaml).
One would take this and modify the renv workflow
(https://github.com/r-lib/actions/blob/v2-branch/setup-renv/action.yaml) to 
somehow use initially just a loop to restore each renv env individually, and 
eventually maybe targets to only restore and reknit changed chapters I suppose.
I don't yet know enough about targets to bother with this.

- You would have to explicitly install these dependencies first:
  - renv?
  - bookdown
  - downlit?
  - bslib?
  - that xml thingy
  - targets

Option 2b: 

## Targets 

```{r}
#### renv_load() - Load the renv library ####
chapter <- "07-renv"

proj_root <- rprojroot::find_root("_bookdown.yml")

renv_path <- paste0(proj_root, "/_renv/", chapter)

message(renv_path)
renv::load(project = renv_path, quiet = FALSE)
```

```{r, child="07-renv/child.Rmd"}
```
